\documentclass[conference]{IEEEtran}
%\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
%\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
%\usepackage[margin=1.5in]{fullpage}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}
%\usepackage{}
\usepackage{color}
\definecolor{Orange}{rgb}{1,0.5,0}
\definecolor{HBGreen}{rgb}{0,0.8,0}
\newcommand{\todo}[1]{\textsf{\textbf{\textcolor{Orange}{[Todo: #1]}}}}
% Macro for writing in the margin comments on what is left to be done.
\newif\ifdraft
               \drafttrue
               %\draftfalse
\ifdraft
\newcounter{ournotecounter}
\newcommand{\ournote}[1]{%
\textsf{\textbf{\textcolor{Orang}{[#1]}}}}
\newcommand{\alnote}[1]{%
\textsf{\textbf{\textcolor{HBGreen}{[#1]}}}}
\typeout{Compiling in draft mode.}
\else
\newcommand{\ournote}[1]{}
\newcommand{\bigournote}[1]{}
\typeout{Compiling in final mode.}
\fi

\title{Estimating vehicle carbon dioxide emissions through smartphone sensors}
%\subtitle{Using mobile sensing data}
\author{\IEEEauthorblockN{Anders Lehmann}
\IEEEauthorblockA{Department for Computer Science\\
University of Aarhus\\
Email: anders@hih.au.dk}
\and
\IEEEauthorblockN{Henrik Blunck}
\IEEEauthorblockA{Department for Computer Science\\
University of Aarhus\\
Email: blunck@cs.au.dk}
\and
\IEEEauthorblockN{Niels Olof Bouvin}
\IEEEauthorblockA{Department for Computer Science\\
University of Aarhus\\
Email: bouvin@cs.au.dk}
\and
\IEEEauthorblockN{Allan Gross}
\IEEEauthorblockA{Department of Business Development and Technology\\
University of Aarhus\\
Email: agr@auhe.au.dk}

}
\date{October 2015}                                           % Activate to display a given date or no date

\begin{document}
\maketitle
\begin{abstract}
Carbon dioxide emissions from transport constitutes a large, and growing, part of the total carbon emissions. We present a model to estimate carbon dioxide emissions from passenger cars on basis of GPSby using GPS data and accelerometer datae gathered from the driver's or passengers' smartphone apps. The model will enable a more detailed emission inventory, both in terms of location and time.\todo{how are location and especially time to be understood here?}
 \todo{move to end:?} As part of an experiment to establish ground truth, a method for measuring fuel consumption without instrumenting vehicles is presented. 
 As part of this estimation model,  aA method for discerning between different driving modes is presented, using the K-means clustering method. This method will increase the accuracy of the emission model by estimation of increased fuel consumption while accelerating and decreased fuel consumption while braking, as well as estimate idle time.

\end{abstract}
\pagenumbering{arabic}	
\todo{fix figures, legends labels, axis}

\todo{niels kommentarer}
\todo{Henriks kommentarer}
\todo{conclusion futurework acceleration}
\todo {models mention kmeans}
\todo{results more in kmeans, relation to emissions}
\todo{results comparison to other methods, hhmm, measurement of accurcy, relation to emissions}


\input{intro}
\input{related}
%\input{mobilesensing}
%\input{emission_models}
%\input{hypoteser}
\input{experiment}
\input{models}
\input{results}
%\input{futurework}
\input{conclusion}
\section*{Acknowledgment}
This work has been supported by The Danish Council for Strategic Research as part of the EcoSense project (11-115331).
\newpage
\pagenumbering{gobble}	
\bibliographystyle{abbrv}
\bibliography{PERCOM16}
\end{document}  












